---
title: "Astronomy"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Astronomy}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(SciViz)
```

While this package only includes two functions for astronomy, both can be very important for dealing with the wide variety of numeric data that astronomers often encounter during their work. 

## Cornerplots 

Cornerplots are often used in astronomy to identify the distributions of numeric variables. Each plot provides a 2d histogram for each pair of variables provided and a 1d histogram that shows the distribution of each variable on its own. An example is shown below. 

```{r}
astroCornerplot(starcatalog)
```

- describe how to interpret the graph 
- describe how to customize the graph, what the options do, link to the color palette website 

## Scatterplots 

- describe what a scatterplot is 

```{r}
astroScatter(starcatalog, "vmag", "bv_color")
```

- describe how to interpret the graph 
- describe how to customize the graph, what the options do, link to the color palette website. 
