---
title: "SciViz"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{SciViz}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This package was designed for scientists to create beautiful and publishable graphs without needing to learn the ins and outs of coding graphs in R. While these functions were created with astronomy, neuroscience, and psychology in mind, they can be used in any fields. 

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, warning = F, message = F}
library(SciViz)
```

## APA Graphs 

### Line 

### Bar 

## Network Plots and Heatmaps 

### Network Plot 

### Heatmap 

## Corner- and Scatterplots

### Cornerplots 

Cornerplots are often used in astronomy to understand the distribution of numeric variables. These are often used to display the results from Markov Chain Monte Carlo (MCMC) simulations, and are used by astronomers to identify if their variables have Gaussian distributions. While those methods are likely familiar to astronomers who may be using this package, even if you aren't sure what an MCMC simulation of a Gaussian distribution is, there are other ways to utilize this package for a better understanding of your data. 

Let's look at an example with the dataset from this package, [starcatalog](). This dataset has information on 8774 stars, and we might be interested in seeing the relationships between the numeric variables in this dataset. Here is how you can make a cornerplot, using all of the default settings. 

```{r}
cornerplot(starcatalog)
```

This plotted all of the numeric variables in the dataset, `bv_color`, `parallax`, and `vmag` against each other in both 2d and 1d histograms. The 1d histograms are shown in purple and show only the distribution of the variable on the x-axis, while the 2d histograms show paired distributions for the variables on the x- and y-axes. Here, we can see that parallax is very right-skewed, which is also clear through the 2d histograms it is a part of, clumping the data vertically downwards. We can see that there are possibly some outliers in this data when looking at the combinations of `bv_color` and `parallax`, as there are a few data points with abnormally high parallax, even though they have values in the normal range for `bv_color`. Additionally, we can see how many points fall within each range by using the colorbar next to the 2d histograms. For example, when examining just `bv_color` and `vmag`, there is a high concentration of stars that have a `vmag` value of around six, with a `bv_color` value of around zero. 

There are many ways you can customize these plots to make them better suit your needs. For example, if you only want to examine the relationships between two of the variables in starcatalog, you can specify them. You can also remove the countor plot that sits on top of the cornerplot, and change the color of both kinds of histograms. Any [`ggplot2` color](https://sape.inf.usi.ch/quick-reference/ggplot2/colour) can be used to change the color of the histograms, and color palette options have been taken from the [colorspace](https://colorspace.r-forge.r-project.org/articles/ggplot2_color_scales.html#available-palettes) package. 

```{r}
cornerplot(starcatalog, varlist = c("vmag", "bv_color"), palette = "Blues", fill="dodgerblue3", contour = FALSE)
```
Here, we have changed the graph so that both histograms have a blue fill/palette, only two of the variables are displayed, and the contour has been removed. 

Further customization can be achieved through changing the number of bins and contour lines. The default number of bins for the histograms is 30, but can be adjusted down to any number of your choosing. Similarly, the default number of contours is 3. The `bins` parameter adjusts the number of bins in both the 1d and 2d histograms, while the `contourBins` parameter is only used when there is a contour plot on top of the 2d histograms.

```{r}
cornerplot(starcatalog, bins = 50, contourBins = 5)
```
In the example above, it is harder to see the distributions because there are so many bins, so be sure to change the `bins` and `contourBins` parameters until you get a result you are happy with. 

### Scatterplots 




